PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
set to NA if missigness

## GLAD demographics
# Read in data
```{r glad dem cols}
glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
dim(glad.dem.raw)
colnames(glad.dem.raw)
```

@@

*Note that scores with missingness will be changed to NA later in the script
```{r gad sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

@@

# Calulate total score
gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
                                        items = glad.gad.raw.id[gad.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.gad.raw.id$gad.sum_score_prepan <- gad.scored_items_prepan$scores

# Look at values
glad.gad.raw.id %>%
  descr(gad.sum_score_prepan,
        stats = "common"
        )
```

@@

```{r sum score cut offs PHQ prepan}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    phq.sum_score_prepan_full =
      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
              NA_real_,
              phq.sum_score_prepan
              )
  )

summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
```

>>>>

# GLAD demographics
## Read in data
```{r glad dem cols}
glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
dim(glad.dem.raw)
colnames(glad.dem.raw)
```

@@

*Note that scores with missingness will be changed to NA later in the script
```{r gad sum score prepan raw}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

@@

# Calulate total score
gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
                                        items = glad.gad.raw.id[gad.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores

# Look at values
glad.gad.raw.id %>%
  descr(gad.sum_score_prepan_raw,
        stats = "common"
        )
```

missingness (NAs per person)

prepandemic
```{r gad prepan missingness}
glad.gad.raw.id <- glad.gad.raw.id %>%
  mutate(
    na_per_person_gad_prepan_raw =         # variable for NA per person
      rowSums(                       
        is.na(.[gad.items_prepan])
      )
  )

glad.gad.raw.id %>%
  freq(na_per_person_gad_prepan_raw,
       cumul = F)
```

```{r gad prepan sum score if missigng items set to NA}
glad.gad.raw.id <- glad.gad.raw.id %>%
  mutate(
    gad.sum_score_prepan =
      if_else(condition = na_per_person_phq_prepan_raw > 0,
              true = NA_real_,
              false = gad.sum_score_prepan,
              missing = NA_real_
              )
  )

summary(glad.gad.raw.id$gad.sum_score_prepan_raw)
summary(glad.gad.raw.id$gad.sum_score_prepan)
```

@@
